The population of long-period exoplanets --- \\ Fully-automated discovery \& characterization of long-period transiting exoplanet candidates in the \kepler\ archive \vspace{-3\baselineskip}

### 2016-06-29 document/ms.tex
updating eb table; words about target selection

\subsection{Target selection}\sectlabel{data}

For the purposes of this \paper, we select the $\sim40,000$ brightest and
quietest G and K dwarfs from the \kepler\ catalog using the following
parameters:
\begin{itemize}
{\item $4200\unit{K} \le T_\mathrm{eff} \le 6100\unit{K}$,}
{\item $R_\star \le 1.15\,R_\odot$,}
{\item $K_p \le 15\unit{mag}$, and}
{\item $\mathrm{CDPP}_{7.5\unit{hrs}} \le 1000\unit{ppm}$.}
\end{itemize}
We also restrict the sample to only include targets with a data span of more
than two years and a duty cycle of better than $0.6$.
Since the \kepler\ data have been searched for shorter period planets
\dfmtodo{CITE Coughlin} and eclipsing binaries \dfmtodo{CITE EB catalog} than
targeted by this project, we censor these previously known targets.
For the known EBs, we simply remove these targets from the candidate list.
For the confirmed and candidate KOIs from \dfmtodo{Coughlin}, we remove data
within 2 transit durations of the known candidates.

>>>>

To limit the scope of this paper while still demonstrating the applicability
of our method, we search the \kepler\ archival light curves of the brightest
and quietest Sun-like stars for long-period transiting exoplanets.
In this section, we describe the target selection process, the parameter
estimation procedure, and present the catalog of discoveries.

\subsection{Target selection}\sectlabel{target-selection}

We select the $\sim40,000$ brightest and quietest G and K dwarfs from the
\kepler\ catalog using the most recent catalog of stellar parameters%
\footnote{Parameters from the \textsf{q1\_q17\_dr24\_stellar} table from the
NASA Exoplanet Archive \citep[][with updates]{Huber:2014}.} and the cuts used
by \citet{Burke:2015}:
\begin{itemize}
{\item $4200\unit{K} \le T_\mathrm{eff} \le 6100\unit{K}$,}
{\item $R_\star \le 1.15\,R_\odot$,}
{\item $\mathrm{data\,span} \ge 2\,\mathrm{years}$,}
{\item $\mathrm{duty\,cycle} \ge 0.6$,}
{\item $K_p \le 15\unit{mag}$, and}
{\item $\mathrm{CDPP}_{7.5\unit{hrs}} \le 1000\unit{ppm}$.}
\end{itemize}
We continue by excluding the light curves of known eclipsing
binaries\footnote{\url{http://keplerebs.villanova.edu/}} \citep{Kirk:2016} and
other known false positives \citep{Coughlin:2016}.
The final catalog contains 39,518 targets and the parameter distribution is
shown in \dfmfig{targets}.

We also restrict the sample to only include targets with a data span of more
than two years and a duty cycle of better than $0.6$.
Since the \kepler\ data have been searched for shorter period planets
\dfmtodo{CITE Coughlin} and eclipsing binaries \dfmtodo{CITE EB catalog} than
targeted by this project, we censor these previously known targets.
For the known EBs, we simply remove these targets from the candidate list.
For the confirmed and candidate KOIs from \dfmtodo{Coughlin}, we remove data
within 2 transit durations of the known candidates.
